## {.center}

::: {style="position: relative; width: 70%; margin: 0 auto;"}

```{r chart-default}
#| fig.width: 6
#| fig.height: 4.5
#| fig-align: center
#| out.width: 85%

gg_line_og <- ggplot(df_psavert, aes(x = date, y = psavert, color = "psavert")) +
  geom_line(linewidth = 0.3) +
  scale_color_manual(values = c("psavert" = brand$gratuitous)) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
  scale_y_continuous(
    limits = function(x) c(0, ceiling(max(x)) * 1.1)
   ) +
  labs(
    title = "Personal Savings Rate by Month in 2009",
    x = "Month",
    y = "Personal Savings Rate (%)",
    caption = "Source: https://fred.stlouisfed.org/series/PSAVERT/",
    color = NULL
  ) +
  # worsen things up a bit by adding a gratuitous legend and plot border
  theme(
    legend.position = "top",
    plot.title.position = "plot",
    plot.caption.position = "plot",
    plot.caption = element_text(size = 8, hjust=0),
    plot.background  = element_rect(linewidth = 0.75, color = "gray40", fill = NA),
    plot.margin = margin(10,10,10,10,"pt"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

gg_line_og

```

::: {.callout-rect .fragment .fade-in-then-out fragment-index=1 style="top: 1.5%; left: 7.5%; width: 1135px; height: 850px;"}
:::

<!--
::: {.callout-oval .fragment .fade-in-then-out fragment-index=2 style="top: 70%; left: 46%; width: 50px; height: 150px; transform: rotate(45deg);"}
:::
-->

::: {.callout-oval .fragment .fade-in-then-out fragment-index=2 style="top: 23%; left: 7.8%; width: 60px; height: 450px;"}
:::

::: {.callout-oval .fragment .fade-in-then-out fragment-index=3 style="top: 9.3%; left: 46%; width: 180px; height: 70px;"}
:::

::: {.callout-oval .fragment .fade-in-then-out fragment-index=4 style="top: 81.5%; left: 47.5%; width: 150px; height: 60px;"}
:::

::: {.callout-line-vertical .fragment .fade-in-then-out fragment-index=5 style="top: 20.8%; left: 31.3%; height: 482px;"}
:::

::: {.callout-line-vertical .fragment .fade-in-then-out fragment-index=5 style="top: 20.8%; left: 34.5%; height: 482px;"}
:::

::: {.callout-line-vertical .fragment .fade-in-then-out fragment-index=5 style="top: 20.8%; left: 37.7%; height: 482px;"}
:::

::: {.fragment}
:::

:::

::: {.notes}
Let's look at a generic, simple line chart. This is the ggplot defaults (made a little bit worse).

There are a lot of redundant or non-data/information pixels here.
:::

## Personal Savings Rate by Month in 2009

::: {style="margin: 0 auto;"}

```{r higher-data-pixel}
#| fig.width: 8
#| fig.height: 4.5
#| fig-align: center
#| out.width: 77%

gg_line_better <- ggplot(df_psavert, aes(x = date, y = psavert)) +
  geom_line(linewidth = 0.8, color=brand$gratuitous) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(
    labels = label_percent(scale = 1),
    breaks = seq(0, 8, by = 2),
    expand = c(0,0),
    limits = function(x) c(0, ceiling(max(x)))
   ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.background = element_rect(fill = brand$bg, color = NA),
    axis.title = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "gray70", linewidth = 0.2),
    axis.text = element_text(family = font_sans_serif, size = 14, color = "gray60"),
    axis.line.x = element_line(color = "gray40", linewidth = 0.4)
  )

gg_line_better
```

:::

::: {.slide-source-footer .muted}
[Source: https://fred.stlouisfed.org/series/PSAVERT/]{.muted}
:::

::: {.notes}
The same data, higher data-pixel ratio. No border, no legend, no redundant axis titles, horizontal month labels.
:::

# We want to make the point as [impossible to miss]{.emphasis} as we can. {background-color="var(--divider-bg)"}

## Personal Savings Rate by Month in 2009

::: {style="margin: 0 auto;"}

```{r higher-data-pixel_repeat}
#| fig.width: 8
#| fig.height: 4.5
#| fig-align: center
#| out.width: 77%

gg_line_better
```

:::

::: {.slide-source-footer .muted}
[Source: https://fred.stlouisfed.org/series/PSAVERT/]{.muted}
:::

::: {.notes}
This is what we had. But...what is it I want to *say* here? We want to make it *impossible to miss*.
:::

## Stimulus payments in [May]{.emphasis} drove [savings spike]{.emphasis}{.nostretch}
::: {.subtitle-slide-text}
Personal saving rate by month: 2009
:::

```{r line-impossible}
#| fig.width: 8
#| fig.height: 4.2
#| fig-align: center
#| out.width: 77%

# Add the highlight spot
df_highlight <- df_psavert |> 
  filter(date == as.Date("2009-05-01")) |> 
  mutate(psavert_callout = "ARRA Payments")
 
gg_line_final <- ggplot(df_psavert, aes(x = date, y = psavert)) +
  geom_line(linewidth = 0.7, color=brand$primary) +
  # The highlighted point
  geom_point(
    data = df_highlight,
    aes(x = date, y = psavert),
    size = 3,
    color = brand$accent
  ) +
  # Left-pointing arrow, positioned to the right of the point
  geom_segment(
    data = df_highlight,
    aes(x = date + 25, xend = date + 6,
        y = psavert, yend = psavert),
    arrow = arrow(length = unit(0.15, "cm"), type = "closed"),
    linewidth = 0.6,
    color = "gray30",
    inherit.aes = FALSE
  ) +
  # Callout text at the tail end of the arrow
  geom_label(
    data = df_highlight,
    aes(x = date + 28, y = psavert, label = psavert_callout),
    hjust = 0,
    vjust = 0.5,
    size = 5,
    family = font_sans_serif,
    color = "gray20", 
    fill = brand$bg,
    label.size = 0
  ) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(
    labels = label_percent(scale = 1),
    breaks = seq(0, 8, by = 2),
    expand = c(0,0),
    limits = function(x) c(0, ceiling(max(x)))
   ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.background = element_rect(fill = brand$bg, color = NA),
    axis.title = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "gray70", linewidth = 0.2),
    axis.text = element_text(family = font_sans_serif, size = 12, color = "gray60"),
    axis.line.x = element_line(color = "gray40", linewidth = 0.4)
  )

gg_line_final
```

::: {.slide-source-footer .muted}
[Source: https://fred.stlouisfed.org/series/PSAVERT/]{.muted}
:::

::: {.notes}
We can really highlight what we're calling out. In this case, we made the title call out exactly what we're showing, and we emphasized in the chart itself that same highlight.
:::
