# What about [tables]{.emphasis}? {background-color="var(--divider-bg)"}

##

::::: {.columns}

::: {.column .slide-body-heading width="40%"}
Europe in 2007
:::

:::: {.column width="60%"}
::: {.raw-table-demo}
```{r table-base}
print(df_europe_2007, n=30)
```
:::
::::

:::::

::: {.slide-source-footer .muted}
[Source: gapminder R package (Gapminder.org, ~2010 excerpt), gdpPercap is constant 2005 Int'l $ (PPP)]{.muted}
:::

::: {.notes}
Sure. This looks *familiar*, but it's brutal on the brain: extra labels at the top, column names using variable names rather than what they represent, no comma-delimiting.
:::

##

```{r}
# Make a version that cleans up the data to be more display-friendly
df_europe_2007_cleaner <- df_europe_2007 |> 
  mutate(pop = round(pop/1000000,1),
         gdpPercap = format(gdpPercap, digits = 1, big.mark=","),
         lifeExp = round(lifeExp, 1)) |> 
  select(Country = "country",
         `Population (M)` = "pop",
         `Life Expectancy` = "lifeExp",
         `GDP per Capita (USD)` = "gdpPercap")

```

:::: {.columns}

::: {.column .slide-body-heading width="40%"}
Europe in 2007
:::

::: {.column .kable-table width="60%"}
```{r table-improve-1}
# Use kable to make a table that has borders for rows and columns and alternating
# striped rows.
df_europe_2007_cleaner |> 
  kable("html", align = c("l", "r", "r", "r"),
        table.attr = 'class="kable-table-borders table-system-font"') |>                     
  kable_styling(full_width = FALSE, position = "center") |>  
  column_spec(1, width = "7cm", bold = TRUE) %>% 
  column_spec(2, width = "5cm") |> 
  column_spec(3, width = "5cm") |> 
  column_spec(4, width = "6cm") |> 
  row_spec(0, bold = TRUE, color = brand$bg, background = brand$primary)
```
:::

::::

::: {.slide-source-footer .muted}
[Source: gapminder R package (Gapminder.org, ~2010 excerpt), GDP per Capita is constant 2005 Int'l $ (PPP)]{.muted}
:::

::: {.notes}
Better? Yes. Probably.
Lots of pixels keeping that data-pixel ratio down: the borders everywhere, the striped rows, ...
:::

##

:::: {.columns}
::: {.column .slide-body-heading width="40%"}
Europe in 2007
:::

::: {.column .kable-table width="60%"}
```{r table-improve-2}
# Make some improvements to the kable version.
df_europe_2007_cleaner |> 
  kable("html", align = c("l", "r", "r", "r"),
        table.attr = 'class="kable-table-light table-system-font"') |>                     
  kable_styling(full_width = FALSE, position = "center") |>  
  column_spec(1, width = "7cm", bold = TRUE) %>% 
  column_spec(2, width = "5cm") |> 
  column_spec(3, width = "5cm") |> 
  column_spec(4, width = "6cm") |> 
  row_spec(0, bold = TRUE, color = brand$primary)
```
:::

::::

::: {.slide-source-footer .muted}
[Source: gapminder R package (Gapminder.org, ~2010 excerpt), GDP per Capita is constant 2005 Int'l $ (PPP)]{.muted}
:::

::: {.notes}
Easier on the eyes. Still... high cognitive load to read and process numbers.
:::

##

:::: {.columns}
::: {.column .slide-body-heading width="40%"}
Europe in 2007
:::

::: {.column .kable-table width="60%"}
```{r table-gt}
#| html-table-processing: none
# Use gt & gtExtras to pair each metric value with an inline bar scaled to the
# largest value in that column. Works from df_europe_2007 (all-numeric), with
# each metric duplicated into a value column and a bar column.
df_europe_2007_gt <- df_europe_2007 |>
  mutate(pop = round(pop/1000000, 1),
         lifeExp = round(lifeExp, 1)) |>
  mutate(pop_bar = pop,
         lifeExp_bar = lifeExp,
         gdpPercap_bar = gdpPercap) |>
  select(country, pop, pop_bar, lifeExp, lifeExp_bar, gdpPercap, gdpPercap_bar)

# Make the table
df_europe_2007_gt |> 
  gt(id = "europe-metrics-tbl") |>
  fmt_number(columns = c(pop, lifeExp), decimals = 1) |>
  fmt_number(columns = gdpPercap, decimals = 0) |>
  gt_plt_bar(column = pop_bar, color = brand$primary, scale_type = "none", width = 45) |>
  gt_plt_bar(column = lifeExp_bar, color = brand$primary, scale_type = "none", width = 28) |>
  gt_plt_bar(column = gdpPercap_bar, color = brand$primary, scale_type = "none", width = 28) |>
  cols_label(country = "",
             pop = "",
             pop_bar = "",
             lifeExp = "",
             lifeExp_bar = "",
             gdpPercap = "",
             gdpPercap_bar = "") |>
  tab_spanner(label = "Country", columns = country, id = "country_span") |>
  tab_spanner(label = "Population (M)", columns = c(pop, pop_bar)) |>
  tab_spanner(label = "Life Expectancy", columns = c(lifeExp, lifeExp_bar)) |>
  tab_spanner(label = "GDP per Capita (USD)", columns = c(gdpPercap, gdpPercap_bar)) |>
  cols_align(align = "left", columns = country) |>
  cols_align(align = "right", columns = c(pop, lifeExp, gdpPercap)) |>
  cols_width(country ~ px(300),
             gdpPercap ~ px(150)) |>
  tab_style(style = cell_text(weight = "bold"),
            locations = cells_body(columns = country)) |>
  tab_style(style = cell_text(color = brand$muted_med),
            locations = cells_body(columns = c(pop, lifeExp, gdpPercap))) |>
  tab_style(style = cell_text(weight = "bold", color = brand$primary),
            locations = cells_column_spanners()) |>
  tab_style(style = cell_text(align = "left"),
                              locations = cells_column_spanners(spanners = "country_span")) |> 
  # Bump body text size specifically (keeps spanner/label size independent)
  tab_style(style = cell_text(size = px(22)),
            locations = cells_body()) |>
  tab_options(table.background.color = brand$bg,
              table.font.size = px(18),
              data_row.padding = px(2),
              column_labels.border.top.style = "hidden",
              column_labels.border.bottom.color = brand$muted,
              table_body.hlines.color = brand$muted,
              table_body.border.bottom.color = brand$muted,
              table.border.top.style = "hidden",
              table.border.bottom.style = "hidden") |>
  opt_css(
    css = "
      #europe-metrics-tbl .gt_col_headings:not(.gt_spanner_row) {
        display: none;
      }
      #europe-metrics-tbl .gt_table .gt_body tr td {
        line-height: 1.4;
      }
    "
  )
```
:::

::::

::: {.slide-source-footer .muted}
[Source: gapminder R package (Gapminder.org, ~2010 excerpt), GDP per Capita is constant 2005 Int'l $ (PPP)]{.muted}
:::

::: {.notes}
Now the eye can compare countries at a glance — the bars carry the magnitude, the numbers are there when you need precision.
:::

##

:::: {.columns}
::: {.column .slide-body-heading width="40%"}
[France]{.emphasis} and the [UK]{.emphasis} were [2007 twinsies]{.emphasis}.
:::

::: {.column .kable-table width="60%"}
```{r table-gt-highlight}
#| html-table-processing: none
# Use gt + gtExtras to pair each metric value with an inline bar scaled to the
# largest value in that column. Works from df_europe_2007 (all-numeric), with
# each metric duplicated into a value column and a bar column.
df_europe_2007_gt <- df_europe_2007 |>
  mutate(pop = round(pop/1000000, 1),
         lifeExp = round(lifeExp, 1)) |>
  mutate(pop_bar = pop,
         lifeExp_bar = lifeExp,
         gdpPercap_bar = gdpPercap) |>
  select(country, pop, pop_bar, lifeExp, lifeExp_bar, gdpPercap, gdpPercap_bar)

# Make the table
# Build once, reuse across all three gt_plt_bar() calls
highlight_countries <- c("France", "United Kingdom")

bar_colors <- dplyr::if_else(
  df_europe_2007_gt$country %in% highlight_countries,
  brand$accent,
  brand$muted
)

df_europe_2007_gt |> 
  gt(id = "europe-metrics-tbl") |>
  fmt_number(columns = c(pop, lifeExp), decimals = 1) |>
  fmt_number(columns = gdpPercap, decimals = 0) |>
  gt_plt_bar(column = pop_bar, color = bar_colors, scale_type = "none", width = 45) |>
  gt_plt_bar(column = lifeExp_bar, color = bar_colors, scale_type = "none", width = 28) |>
  gt_plt_bar(column = gdpPercap_bar, color = bar_colors, scale_type = "none", width = 28) |>
  cols_label(country = "",
             pop = "",
             pop_bar = "",
             lifeExp = "",
             lifeExp_bar = "",
             gdpPercap = "",
             gdpPercap_bar = "") |>
  tab_spanner(label = "Country", columns = country, id = "country_span") |>
  tab_spanner(label = "Population (M)", columns = c(pop, pop_bar)) |>
  tab_spanner(label = "Life Expectancy", columns = c(lifeExp, lifeExp_bar)) |>
  tab_spanner(label = "GDP per Capita (USD)", columns = c(gdpPercap, gdpPercap_bar)) |>
  cols_align(align = "left", columns = country) |>
  cols_align(align = "right", columns = c(pop, lifeExp, gdpPercap)) |>
  cols_width(country ~ px(300),
             gdpPercap ~ px(150)) |>
  tab_style(style = cell_text(weight = "bold", color = brand$muted_med),
            locations = cells_body(columns = country)) |>
  tab_style(style = cell_text(color = brand$muted_med),
            locations = cells_body(columns = c(pop, lifeExp, gdpPercap))) |>
  tab_style(style = cell_text(weight = "bold", color = brand$primary),
            locations = cells_column_spanners()) |>
  tab_style(style = cell_text(align = "left"),
                              locations = cells_column_spanners(spanners = "country_span")) |> 
  # Country name color override for the two highlighted rows
  tab_style(style = cell_text(color = brand$accent, weight = "bold"),
            locations = cells_body(columns = c(country, pop, lifeExp, gdpPercap), 
                                   rows = country %in% highlight_countries)) |>
  # Bump body text size specifically (keeps spanner/label size independent)
  tab_style(style = cell_text(size = px(22)),
            locations = cells_body()) |>
  tab_options(table.background.color = brand$bg,
              table.font.size = px(18),
              data_row.padding = px(2),
              column_labels.border.top.style = "hidden",
              column_labels.border.bottom.color = brand$muted,
              table_body.hlines.color = brand$muted,
              table_body.border.bottom.color = brand$muted,
              table.border.top.style = "hidden",
              table.border.bottom.style = "hidden") |>
  opt_css(
    css = "
      #europe-metrics-tbl .gt_col_headings:not(.gt_spanner_row) {
        display: none;
      }
      #europe-metrics-tbl .gt_table .gt_body tr td {
        line-height: 1.4;
      }
    "
  )
```
:::

::::

::: {.slide-source-footer .muted}
[Source: gapminder R package (Gapminder.org, ~2010 excerpt), GDP per Capita is constant 2005 Int'l $ (PPP)]{.muted}
:::

::: {.notes}
And now let's make it impossible to miss. What I'm probably doing here is making a claim that will equally upset the British and the French.
:::


