# What about [tables]{.emphasis}? {background-color="var(--divider-bg)"}

##

:::: {.columns}

::: {.column width="40%" .slide-body-heading}
Europe in 2007
:::

::: {.column width="60%"}
::: {.raw-table-demo}
```{r table-base}
print(df_europe_2007, n=30)
```
:::
:::

::::

::: {.slide-source-footer .muted}
[Source: gapminder R package (Gapminder.org, ~2010 excerpt), gdpPercap is constant 2005 Int'l $ (PPP)]{.muted}
:::

::: {.notes}
Sure. This looks *familiar*, but it's brutal on the brain: extra labels at the top, column names using variable names rather than what they represent, no comma-delimiting.
:::

##

```{r}
# Make a version that cleans up the data to be more display-friendly
df_europe_2007_cleaner <- df_europe_2007 |> 
  mutate(pop = round(pop/1000000,1),
         gdpPercap = format(gdpPercap, digits = 1, big.mark=","),
         lifeExp = round(lifeExp, 1)) |> 
  select(Country = "country",
         `Population (M)` = "pop",
         `Life Expectancy` = "lifeExp",
         `GDP per Capita (USD)` = "gdpPercap")

```

:::: {.columns}

::: {.column width="40%" .slide-body-heading}
Europe in 2007
:::

::: {.column width="60%" .kable-table}
```{r table-improve-1}
# Use kable to make a table that has borders for rows and columns and alternating
# striped rows.
df_europe_2007_cleaner |> 
  kable("html", align = c("l", "r", "r", "r"),
        table.attr = 'class="kable-table-borders"') |>                     
  kable_styling(full_width = FALSE, position = "center") |>  
  column_spec(1, width = "7cm", bold = TRUE) %>% 
  column_spec(2, width = "5cm") |> 
  column_spec(3, width = "5cm") |> 
  column_spec(4, width = "6cm") |> 
  row_spec(0, bold = TRUE, color = brand$bg, background = brand$primary)
```
:::

::::

::: {.slide-source-footer .muted}
[Source: gapminder R package (Gapminder.org, ~2010 excerpt), GDP per Capita is constant 2005 Int'l $ (PPP)]{.muted}
:::

::: {.notes}
Better? Yes. Probably.
Lots of pixels keeping that data-pixel ratio down: the borders everywhere, the striped rows, ...
:::

##

:::: {.columns}
::: {.column width="40%" .slide-body-heading}
Europe in 2007
:::

::: {.column width="60%" .kable-table}
```{r table-improve-2}
# Make some improvements to the kable version.
df_europe_2007_cleaner |> 
  kable("html", align = c("l", "r", "r", "r"),
        table.attr = 'class="kable-table-light"') |>                     
  kable_styling(full_width = FALSE, position = "center") |>  
  column_spec(1, width = "7cm", bold = TRUE) %>% 
  column_spec(2, width = "5cm") |> 
  column_spec(3, width = "5cm") |> 
  column_spec(4, width = "6cm") |> 
  row_spec(0, bold = TRUE, color = brand$primary)
```
:::

::::

::: {.slide-source-footer .muted}
[Source: gapminder R package (Gapminder.org, ~2010 excerpt), GDP per Capita is constant 2005 Int'l $ (PPP)]{.muted}
:::

::: {.notes}
Better? Yes. Probably.
Lots of pixels keeping that data-pixel ratio down: the borders everywhere, the striped rows, ...
:::

