# What about [tables]{.emphasis}? {background-color="var(--divider-bg)"}

## {.center}

THIS SLIDE IS IN WORK (HASN'T REALLY BEEN TOUCHED YET)

```{r table-before}

# The "before": default-ish gt table with heavy fills, borders, and banding
df_continents |>
  gt() |>
  cols_label(
    continent    = "Continent",
    countries    = "Countries",
    mean_lifeExp = "Mean Life Expectancy",
    total_pop    = "Total Population"
  ) |>
  fmt_number(columns = mean_lifeExp, decimals = 1) |>
  fmt_number(columns = total_pop, decimals = 0) |>
  tab_options(
    table.font.size = px(34),
    column_labels.background.color = brand$gratuitous,
    row.striping.include_table_body = TRUE,
    table_body.hlines.width = px(2),
    table_body.vlines.width = px(2),
    table_body.vlines.style = "solid",
    table.border.top.width = px(3),
    table.border.bottom.width = px(3)
  ) |>
  opt_row_striping()

```

::: {.notes}
Quick hit: before / after…
:::

## (Increase the data-pixel ratio of) A table {visibility="uncounted"}

THIS SLIDE IS IN WORK (HASN'T REALLY BEEN TOUCHED YET)

```{r table-after}

# The "after": same data, minimal ink — light rules only where they aid scanning
df_continents |>
  gt() |>
  cols_label(
    continent    = "Continent",
    countries    = "Countries",
    mean_lifeExp = "Mean Life Expectancy",
    total_pop    = "Total Population"
  ) |>
  fmt_number(columns = mean_lifeExp, decimals = 1) |>
  fmt_number(columns = total_pop, decimals = 0) |>
  tab_options(
    table.font.size = px(34),
    table.background.color = brand$bg,
    column_labels.border.bottom.width = px(2),
    column_labels.border.bottom.color = brand$dark,
    column_labels.border.top.style = "hidden",
    table_body.hlines.style = "hidden",
    table.border.bottom.style = "hidden"
  )

```

## [Possible Bonus] A table…that can be processed without reading #s

THIS SLIDE IS IN WORK (HASN'T REALLY BEEN TOUCHED YET)

*[Placeholder: same continent table with horizontal bars embedded in the
Total Population column — likely built with `gt` + `gtExtras::gt_plt_bar()`.
To be built.]*

::: {.notes}
Not strictly data-pixel ratio territory, but is a cognitive load reducer: add
horizontal bars in using a gt table.
:::
