# Let's talk about [showing code]{.emphasis}! {background-color="var(--divider-bg)"}

## Predicting the body mass of penguins

```{r code-before}
#| echo: true
#| eval: false

penguins_clean <- penguins |>
  drop_na(body_mass_g, flipper_length_mm, bill_length_mm, bill_depth_mm) |>
  mutate(body_mass_kg = body_mass_g / 1000,
         species = as.factor(species),
         island = as.factor(island),
         sex = as.factor(sex))

model_spec <- lm(body_mass_kg ~ flipper_length_mm + bill_length_mm +
                   bill_depth_mm + species + sex,
                 data = penguins_clean)

model_summary <- broom::tidy(model_spec, conf.int = TRUE, conf.level = 0.95)

model_summary |>
  filter(term != "(Intercept)") |>
  arrange(desc(abs(estimate)))
```

::: {.notes}
This is the default. It may seem fine on your screen now, but it WILL BE TOO MUCH
and it WILL BE TOO SMALL when presented
:::

## Predicting the body mass of penguins

::: {.code-size-1}
```{r code-after-1}
#| echo: true
#| eval: false

penguins_clean <- penguins |>
  drop_na(body_mass_g, flipper_length_mm, bill_length_mm, bill_depth_mm) |>
  mutate(body_mass_kg = body_mass_g / 1000,
         species = as.factor(species),
         island = as.factor(island),
         sex = as.factor(sex))

model_spec <- lm(body_mass_kg ~ flipper_length_mm + bill_length_mm +
                   bill_depth_mm + species + sex,
                 data = penguins_clean)

model_summary <- broom::tidy(model_spec, conf.int = TRUE, conf.level = 0.95)

model_summary |>
  filter(term != "(Intercept)") |>
  arrange(desc(abs(estimate)))
```
:::

::: {.notes}
This is better.
:::

## Predicting the body mass of penguins

::: {.code-size-2}
```{r code-after-2}
#| echo: true
#| eval: false

penguins_clean <- penguins |>
  drop_na(body_mass_g, flipper_length_mm, bill_length_mm, bill_depth_mm) |>
  mutate(body_mass_kg = body_mass_g / 1000,
         species = as.factor(species),
         island = as.factor(island),
         sex = as.factor(sex))

model_spec <- lm(body_mass_kg ~ flipper_length_mm + bill_length_mm +
                   bill_depth_mm + species + sex,
                 data = penguins_clean)

model_summary <- broom::tidy(model_spec, conf.int = TRUE, conf.level = 0.95)

model_summary |>
  filter(term != "(Intercept)") |>
  arrange(desc(abs(estimate)))
```
:::

::: {.notes}
Even better
:::

## Predicting the body mass of penguins
[Prepare the data]{.subtitle-slide-text}

::: {.code-size-2}
```{r code-after-3}
#| echo: true
#| eval: false
#| code-line-numbers: "1-6"

penguins_clean <- penguins |>
  drop_na(body_mass_g, flipper_length_mm, bill_length_mm, bill_depth_mm) |>
  mutate(body_mass_kg = body_mass_g / 1000,
         species = as.factor(species),
         island = as.factor(island),
         sex = as.factor(sex))

model_spec <- lm(body_mass_kg ~ flipper_length_mm + bill_length_mm +
                   bill_depth_mm + species + sex,
                 data = penguins_clean)

model_summary <- broom::tidy(model_spec, conf.int = TRUE, conf.level = 0.95)

model_summary |>
  filter(term != "(Intercept)") |>
  arrange(desc(abs(estimate)))
```
:::

::: {.notes}
Make it impossible to ignore
:::

## Predicting the body mass of penguins
[Build the model]{.subtitle-slide-text}

::: {.code-size-2}
```{r code-after-4}
#| echo: true
#| eval: false
#| code-line-numbers: "8-10"

penguins_clean <- penguins |>
  drop_na(body_mass_g, flipper_length_mm, bill_length_mm, bill_depth_mm) |>
  mutate(body_mass_kg = body_mass_g / 1000,
         species = as.factor(species),
         island = as.factor(island),
         sex = as.factor(sex))

model_spec <- lm(body_mass_kg ~ flipper_length_mm + bill_length_mm +
                   bill_depth_mm + species + sex,
                 data = penguins_clean)

model_summary <- broom::tidy(model_spec, conf.int = TRUE, conf.level = 0.95)

model_summary |>
  filter(term != "(Intercept)") |>
  arrange(desc(abs(estimate)))
```
:::

::: {.notes}
Make it impossible to ignore
:::

## Predicting the body mass of penguins
[View the results]{.subtitle-slide-text}

::: {.code-size-2}
```{r code-after-5}
#| echo: true
#| eval: false
#| code-line-numbers: "12-16"

penguins_clean <- penguins |>
  drop_na(body_mass_g, flipper_length_mm, bill_length_mm, bill_depth_mm) |>
  mutate(body_mass_kg = body_mass_g / 1000,
         species = as.factor(species),
         island = as.factor(island),
         sex = as.factor(sex))

model_spec <- lm(body_mass_kg ~ flipper_length_mm + bill_length_mm +
                   bill_depth_mm + species + sex,
                 data = penguins_clean)

model_summary <- broom::tidy(model_spec, conf.int = TRUE, conf.level = 0.95)

model_summary |>
  filter(term != "(Intercept)") |>
  arrange(desc(abs(estimate)))
```
:::

::: {.notes}
Make it impossible to ignore
:::
