---
title: "Revenue by Month — Three Theme Treatments"
format:
  html:
    embed-resources: true
    toc: false
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(ggthemes)
library(scales)
```

## The Data

A synthetic 13-month revenue series with a gentle upward trend and realistic
month-to-month variation. Median revenue is set at \$20 million.

```{r data}
set.seed(42)

# Build a trend + noise series, then rescale so the median lands at $20M
n <- 13
trend  <- seq(0, 1, length.out = n)          # gentle upward slope
noise  <- rnorm(n, mean = 0, sd = 0.18)      # realistic variation
raw    <- trend + noise

# Rescale: shift so median = 0, scale so spread feels natural, then add $20M
raw_centered <- raw - median(raw)
revenue_raw  <- raw_centered * 3e6 + 20e6    # ~$3M std dev around $20M

df <- tibble(
  month   = seq(as.Date("2024-01-01"), by = "month", length.out = n),
  revenue = revenue_raw
)

# Quick look
df |> mutate(revenue_M = scales::dollar(revenue / 1e6, suffix = "M"))
```

---

## Chart 1 — ggplot2 Defaults

No `theme()` call at all; pure out-of-the-box ggplot2.

```{r chart-default, fig.width=9, fig.height=5}
p_base <- ggplot(df, aes(x = month, y = revenue)) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 2.5) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
  scale_y_continuous(
    labels = label_dollar(scale = 1e-6, suffix = "M"),
    limits = c(0, NA)
  ) +
  labs(
    title   = "Monthly Revenue",
    subtitle = "13-month trend | Jan 2024 – Jan 2025",
    x       = NULL,
    y       = "Revenue"
  )

p_base
```

---

## Chart 2 — Tufte Theme (`ggthemes`)

Edward Tufte's minimalist aesthetic: no background, muted grid, range-frame axes.

```{r chart-tufte, fig.width=9, fig.height=5}
p_base +
  theme_tufte(base_size = 13) +
  geom_rangeframe(color = "grey30")   # Tufte-style axis end-caps
```

---

## Chart 3 — Maximum Data-Pixel Ratio

Every non-data element stripped away: no panel background, no grid lines, no
axis ticks, no axis titles, minimal axis text. The data line is the only thing
left to look at.

```{r chart-max-dpr, fig.width=9, fig.height=5}
p_base +
  labs(title = NULL, subtitle = NULL, x = NULL, y = NULL) +
  theme(
    # Remove all panel elements
    panel.background  = element_blank(),
    panel.grid.major  = element_blank(),
    panel.grid.minor  = element_blank(),
    panel.border      = element_blank(),

    # Remove axis infrastructure
    axis.ticks        = element_blank(),
    axis.line         = element_blank(),

    # Minimal axis text — just enough to orient the reader
    axis.text.x       = element_text(size = 9, color = "grey50", margin = margin(t = 4)),
    axis.text.y       = element_text(size = 9, color = "grey50", margin = margin(r = 4)),

    # Strip the plot frame entirely
    plot.background   = element_blank(),

    # Tight margins
    plot.margin       = margin(8, 8, 8, 8)
  )
```
